Automatic Matching of Bullet Lands

### 2015-12-28 imaging-paper.Rnw
fixed problem with levels

<<prob.ratios, echo=FALSE>>=
library(reshape2)
dens.stats <- dm %>% group_by(var, variable) %>% mutate(
  sum = sum(value),
  up = cumsum(value)/sum,
  down = 1 - cumsum(value)/sum
)
ratios <- dens.stats %>% group_by(var, x) %>% summarise(
  upper = sum(up[variable=="KM"])/sum(up[variable=="KNM"]),
  lower = sum(down[variable=="KM"])/sum(down[variable=="KNM"])
)
rm <- melt(ratios, measure.var=c("upper", "lower"))
levels(rm$variable) <- c("P(X < c | KM) / P(X < c | KNM)", "P(X > c | KM) / P(X > c | KNM)")
qplot(x, value, colour=variable,  data=rm) + facet_wrap(~var, scales="free") + scale_y_log10() + theme_bw() + geom_hline(yintercept=1) + scale_colour_brewer(palette="Set2") + ylab("Probability Ratios")
@

>>>>

<<prob.ratios, echo=FALSE>>=
library(reshape2)
dens.stats <- dm %>% group_by(var, variable) %>% mutate(
  sum = sum(value, na.rm=TRUE),
  up = cumsum(value)/sum,
  down = 1 - cumsum(value)/sum
)
levels(dens.stats$variable) <- c("KM", "KNM")
ratios <- dens.stats %>% group_by(var, x) %>% summarise(
  lower = sum(up[variable=="KM"], na.rm=TRUE)/sum(up[variable=="KNM"], na.rm=TRUE),
  upper = sum(down[variable=="KM"], na.rm=TRUE)/sum(down[variable=="KNM"], na.rm=TRUE)
)
rm <- melt(ratios, measure.var=c("lower", "upper"))
levels(rm$variable) <- c("P(X < c | KM) / P(X < c | KNM)", "P(X > c | KM) / P(X > c | KNM)")
qplot(x, value, colour=variable,  data=rm) + facet_wrap(~var, scales="free") + scale_y_log10() + theme_bw() + geom_hline(yintercept=1) + scale_colour_brewer(palette="Set2") + ylab("Probability Ratios")
@
